---
title: "Leaflet example"
author: "Bill Kelemen"
date: "1/21/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown document contains an example of leaflet usage. 

The example is a map of all Roger Waters concerts in North America in 2017. Details of the concerts can be views on the official [web site](http://www.rogerwaters.com).  

First we'll read a csv file that was prepared with the data. This file was created by a separate R script [get_concerts.R](https://github.com/bkelemen56/R-leaflet-example/blob/master/get_concerts.R). This script performs data scraping on the official site for the table of concerts, and then uses Google map API to retrieve the latitud/longitud coordinates for each venue.

```{r cars}
concerts <- read.csv("data/concerts.csv")
```

The leaflet map is created with the following R code. The map will show the locations of the concerts, clustering them depending on the zoom level. Popups are used to display the venue, concert date and city.

```{r leaflet_concerts2}
library(leaflet)

pop_html <- paste0('<b>', concerts$VENUE, '</b><br/>',
                   concerts$DATE, ', 2017<br/>',
                   concerts$CITY, '<br/>')

concerts %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(clusterOptions = markerClusterOptions(), pop = pop_html)
```

